Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
p2

Additionally, it is noted that a sample triplet will be augmented into a
sextuplet (both benign and adversarial examples) during adversarial training.
%
In this case, the \emph{intra-class} structure can be enforced, which has been
neglected by existing methods.
%
Since some existing attacks aim to change the sample rankings in the same
class~\cite{advrank},
%
we propose a simple \emph{intra-class} structure loss term for adversarial
training, which is expected to further improve robustness.

% evaluation and conclusion
Comprehensive experiments are conducted on three commonly used DML datasets,
namely CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford Online
Product~\cite{sop}.
%
The proposed method overwhelmingly outperforms the state-of-the-art defense in
terms of training cost, robustness, as well as the performance on benign
examples.

@@

% contributions
In summary, our contributions include proposing:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
		tool to create adversarial example triplets for subsequent adversarial
		training of a DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
		a pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
		model robustness and adversarial training efficiency, while such structure is
		neglected by existing methods. 
		%
\end{enumerate}

@@

\textbf{Adversarial Defense.}
%
Various defenses are proposed to counter the attacks.
%
However, defenses incurring gradient masking
lead to a false sense of robustness~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} is compromised in~\cite{cw}.
%
Ensemble of weak defenses is not
robust~\cite{ensembleweak}.
%
Other defenses such as input
preprocessing~\cite{deflecting}, or a randomization~\cite{self-ensemble} are proposed.
%
But many of them are still susceptible to adaptive attacks~\cite{adaptive}.
%
Of all defenses, adversarial training~\cite{madry} consistently remains to be one of the
most effective
methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter},
but suffers from high training cost~\cite{freeat,fastat,yopo}, performance drop on
benign examples~\cite{odds,geometry,onmanifold}, and overfitting on adversarial examples~\cite{bagoftricks,overfitting}.

>>>>

Additionally, it is noted that a sample triplet will be augmented into a
sextuplet (both benign and adversarial examples) during adversarial training.
%
In this case, the \emph{intra-class} structure can be enforced, which has been
neglected by existing methods.
%
Since some existing attacks aim to change the sample rankings in the same
class~\cite{advrank},
%
we propose a simple \emph{intra-class} structure loss term for adversarial
training, which is expected to further improve adversarial robustness.

% evaluation and conclusion
Comprehensive experiments are conducted on three commonly used DML datasets,
namely CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford Online
Product~\cite{sop}.
%
The proposed method overwhelmingly outperforms the state-of-the-art defense in
terms of robustness, training efficiency, as well as the performance on benign
examples.

@@

% contributions
In summary, our contributions include proposing:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) as a flexible and efficient
		tool to create adversarial example triplets for subsequent adversarial
		training of a DML model.
		%
	\item \textit{Linear Gradual Adversary} (LGA) as a Graduate Adversary, \ie,
		a pseudo-hardness function for HM, which incorporates our empirical
		observations and can balance the training objectives during the
		training process.
		%
	\item \textit{Intra-Class Structure} (ICS) loss term to further improve
		model robustness and adversarial training efficiency, while such structure is
		neglected by existing defenses. 
		%
\end{enumerate}

@@

\textbf{Adversarial Defense.}
%
Various defenses are proposed to counter the attacks.
%
However, defenses incurring gradient masking
lead to a false sense of robustness~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} is compromised in~\cite{cw}.
%
Ensemble of weak defenses is not
robust~\cite{ensembleweak}.
%
Other defenses such as input
preprocessing~\cite{deflecting}, or randomization~\cite{self-ensemble} are proposed.
%
But many of them are still susceptible to adaptive attacks~\cite{adaptive}.
%
Of all defenses, adversarial training~\cite{madry} consistently remains to be one of the
most effective
methods~\cite{bilateral,advtrain-triplet,benchmarking,smoothat,trades,robustwrn,weightperturb,featurescatter},
but suffers from high training cost~\cite{freeat,fastat,yopo}, performance drop on
benign examples~\cite{odds,geometry,onmanifold}, and overfitting on adversarial examples~\cite{bagoftricks,overfitting}.
